---
title: "Homework#3"
author: "Group 2"
date: '2022-08-10'
output: pdf_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```

Part 1
1. Using read.csv() function import SW_EpisodeIV.txt file into R. You must get something like this:
## Rows: 1,011
## Columns: 2
## $ character <chr> "THREEPIO", "THREEPIO", "THREEPIO", "THREEPIO", "THREEPIO...
## $ dialogue <chr> "Did you hear that? They've shut down the main reactor. ...

```{r p1.1, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
dataframe = read.csv("SW_EpisodeIV.txt",sep= " ")
str(dataframe)

```
2. Using dialogue column create new column named  where all punctuation will be removed.
Then created new column called lower_dialogue where all words will be converted to lowercase. You
must get something like this:
## Rows: 1,011
## Columns: 4
## $ character <chr> "THREEPIO", "THREEPIO", "THREEPIO", "THREEPIO", "TH...
## $ dialogue <chr> "Did you hear that? They've shut down the main rea...
## $ string_dialogue <chr> "Did you hear that Theyve shut down the main react...
## $ lower_dialogue <chr> "did you hear that theyve shut down the main react...

```{r p1.2, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
dataframe$string_dialogue = gsub("[^[:alnum:][:space:]']", "", dataframe$dialogue)
dataframe$string_dialogue = gsub("'", '',dataframe$string_dialogue)
dataframe$lower_dialogue = tolower(dataframe$string_dialogue)
str(dataframe)
```
3. Create new vector named words_vector where all words from lower_dialogue column will be added
into your vector. You can use str_split() and make sure to remove empty strings like "" and english
stopwords. Print first 10 elements from your words_vector.
```{r p1.3, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
library(stringr)
library(tm)
words_vector = str_split(dataframe$lower_dialogue," ",simplify = TRUE)
words_vector <- removeWords(words_vector, words = stopwords(kind = "en"))
words_vector =str_subset(words_vector, ".+")
print(words_vector[1:10])
```

4. Remove duplicates from your words_vector and store in vector named vocabulary.
If you did everything correct you will have 5955 observations in words_vector and 1706 observations in
vocabulary vector.

```{r p1.3, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
vocabulary = unique(words_vector)
print(length(words_vector))
print(length(vocabulary))

```